\TitlePt

### 2016-03-18 conclusion.tex
Final conclusion paragraph
Say that all code and data are available.

We have developed two open-source software packages that implement the
components required for building an inversion method: forward modeling,
optimization, and regularization.
We used these components to develop a fast gravity inversion method to estimate
the depth of the crust-mantle interface (the Moho) in a spherical
approximation.
We then applied the proposed method to estimate the Moho depth for South
America.

@@

>>>>

We have developed two open-source software packages that implement the
components required for building an inversion method: forward modeling,
optimization, and regularization.
We used these components to develop a fast gravity inversion method to estimate
the depth of the crust-mantle interface (the Moho) in a spherical
approximation.
We then applied the proposed method to estimate the Moho depth for South
America.
Both software packages, the source code for the gravity inversion, and all
associated data are freely available on the Internet through various websites.

@@

In conclusion,
we have successfully applied the algorithms and software foundation developed
here to solve a geophysical inverse problem.
This application demonstrates that the same approach can be used to aid the
development of new inversion methods in the future.
In addition, both software packages were successful in gaining third-party
users.
\textit{Fatiando a Terra}, in particular, was able to gather other developers
to contribute source code to the software.
This will enable the continued growth of the project and is only possible
because the project is open-source.
